### 2018-11-03 article-gweil.tex
Crap

\begin{abstract}
In arithmetic geometry, we distinguish between local zeta functions (attached to schemes in positive characteristic) and global zeta functions (attached to schemes in characteristic zero). Local zeta functions have a highly constrained structure, governed by the four Weil conjectures (rationality, functional equation, local Riemann hypothesis and connection to Betti numbers).

>>>>

\begin{abstract}
In arithmetic geometryy, we distinguish between local zeta functions (attached to schemes in positive characteristic) and global zeta functions (attached to schemes in characteristic zero). Local zeta functions have a highly constrained structure, governed by the four Weil conjectures (rationality, functional equation, local Riemann hypothesis and connection to Betti numbers).
